Humann2 bar plot by myself

### 2019-10-24 scripts/01_clean_pheno.Rmd
update

```{r}
# the newest pheno table from M
# this sheet have nice sampleids for the samples, and also this is the table has all of the info
phe_M <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 10172019.xlsx',
                    sheet = 5)
```

```{r}
# selecting the columns relavant to this study
phe_M_clean <- phe_M %>% 
   rename_all(funs(str_replace_all(., ' \\(.+$','') %>% 
    str_replace_all(., ' ','_') %>% 
    str_replace(., ':','_'))) %>% 
  # select the columns that may be relavant
  select(Sampleid = Baseline_Sample_ID, 
         Censor_YN,
         Censor_reason,
         CR, 
         ORR, 
         Toxicity, 
         Disease_Status_CAR = Key__Patient_Disease_Status_at_CAR, 
         Disease_Class, 
         CAR_Group) %>% 
  filter(is.na(Censor_reason)) %>% 
  # remove this one record that doesn't seem to be a valid record at all
  filter(!is.na(CR))

@@

```{r}
# loading the table from John to see how many samples we actually have shotgun data
have_sg <- read_csv('../data/baselinesforAngel10032019.csv') %>% 
  filter(shotgun_YN == 'yes') %>% 
  # removig 1943A cuz its low quality
  filter(sample_id != '1943A') %>% 
  # THERE ARE THREE THAT ARE CURRENTLY BEING SEQUENCED, WE DON'T HAVE YET!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
  filter(!sample_id %in% c('161','171','173'))

@@

ggvenn(two)      
```
```{r}
# write out the overlap sampleid cuz that's gonna be the sample_names in use on the cluster for normalization
intersect(have_sg$sample_id, phe_M_clean$Sampleid) %>% 
  write.table('../data/input_for_cluster_sampleid/valid_sample_names.txt', col.names = F, row.names = F, quote = F)
```

>>>>

```{r}
# the newest pheno table from M
# this sheet have nice sampleids for the samples, and also this is the table has all of the info
phe_M <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 10222019.xlsx',
                    sheet = 5)
```

```{r}
# selecting the columns relavant to this study
phe_M_clean <- phe_M %>% 
   rename_all(funs(str_replace_all(., ' \\(.+$','') %>% 
    str_replace_all(., ' ','_') %>% 
    str_replace(., ':','_'))) %>% 
  # select the columns that may be relavant
  select(Sampleid = Baseline_Sample_ID, 
         Censor_reason,
         CR, 
         ORR, 
         Toxicity, 
         Disease_Status_CAR = Key__Patient_Disease_Status_at_CAR, 
         Disease_Class, 
         CAR_Group) %>% 
  filter(is.na(Censor_reason))

@@

```{r}
# loading the table from John to see how many samples we actually have shotgun data
have_sg <- read_csv('../data/baselinesforAngel10032019.csv') %>% 
  filter(shotgun_YN == 'yes') %>% 
  # removig 1943A cuz its low quality
  filter(sample_id != '1943A') %>% 
  # 171 is back, removing the the other two that doesn't make to the final valid sample
  filter(!sample_id %in% c('161','173'))

@@

ggvenn(two)      
```

```{r}
# write out the overlap sampleid cuz that's gonna be the sample_names in use on the cluster for normalization
intersect(have_sg$sample_id, phe_M_clean$Sampleid) %>% 
  write.table('../data/input_for_cluster_sampleid/valid_sample_names.txt', col.names = F, row.names = F, quote = F)
```

### 2019-10-24 scripts/06_lefse_res_ggplot.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r}
feature %>% 
  split(.$group) %>% 
  map(~  ggplot(data = ., aes(x = reorder(pathway, score), y = score, fill = direction)) +
  geom_bar(stat='identity') +
  coord_flip() +
  scale_color_manual(values = c('#00468B', '#EC0000'))  +
  scale_fill_manual(values = c('#00468B', '#EC0000')) +
  theme_minimal() +
  theme(axis.title.y  = element_blank(), 
        legend.position="bottom") +
  labs(title = str_glue('Response to class (with subclass): {.$group}') ,
       y = 'Score')+ 
  ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to class (with subclass): {.$group}.pdf'), device = 'pdf', width = 15, height = 6, dpi = 300))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(grid)
library(cowplot)
library(ggpubr)
```

@@

```{r}
feature %>% 
  filter(str_detect(group, pattern = 'Disease_Class$')) %>% 
  split(.$group) %>% 
  map(~  ggplot(data = ., aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#00468B', '#EC0000'))  +
            scale_fill_manual(values = c('#00468B', '#EC0000')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to class') ,
                 y = 'Score')+ 
            ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to class {.$group}.pdf'), device = 'pdf', width = 15, dpi = 300))

@@

```{r}
CR <- feature %>% 
  filter(str_detect(group, pattern = 'Disease_Class$')) %>% 
  filter(group == 'CR__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#00468B', '#EC0000'))  +
            scale_fill_manual(values = c('#00468B', '#EC0000')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Complete Response') ,
                 y = 'Score')

tox <- feature %>% 
  filter(str_detect(group, pattern = 'Disease_Class$')) %>% 
  filter(group == 'Toxicity__Disease_Class') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar(position = position_dodge2(preserve = "single"), stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#00468B', '#EC0000'))  +
            scale_fill_manual(values = c('#00468B', '#EC0000')) +
            theme_minimal() +
            theme(axis.title.y  = element_blank(), 
                  legend.position="bottom") +
            labs(title = str_glue('Response to Toxicity') ,
                 y = 'Score')

g <- plot_grid(CR, tox,
          nrow = 2, 
          align = 'hv',
          labels = 'AUTO',
          axis = 'b')  +
  ggsave('../figs/dtes.jpg', width = 13, height = 12, dpi = 300)
```

### 2019-10-24 scripts/09_barplot_myself.Rmd
update

```{r}
# pheno table 
pheno <- read_csv('../data/cleaned_pheno/current_pheno.csv')%>% 
  filter(Sampleid %in% valid_s$X1) %>% 
  select(-Censor_YN, -Censor_reason )

>>>>

```{r}
# pheno table 
valid_s <- read_table('../data/input_for_cluster_sampleid/valid_sample_names.txt', col_names = F)

pheno <- read_csv('../data/cleaned_pheno/current_pheno.csv')%>% 
  filter(Sampleid %in% valid_s$X1) %>% 
  select(-Censor_YN, -Censor_reason )
